% Lastname, Firstname. Title of Book. City of Publication: Publisher, Year of Publication. Medium of Publication.
% Author(s). "Title of Article." Title of Journal Volume.Issue (Year): pages. Medium of publication.
\paragraph{}
Birungi, Patricia. "Stereotype - Vorurteile". \emph{Cultural Studies - Patricia Birungi}. 14 Jun. 2001. Web. 3 Jul. 2012. \url{<http://patriciabirungi.wordpress.com/2011/06/14/stereotype-vorurteile/>}.
\paragraph{}
During, Simon. \emph{Cultural Studies: A Critical Introduction}. London: Routledge, 2005. Print.
\paragraph{}
McGarty, C., Yzerbyt, V. Y., and R. Spears. "Social, cultural and cognitive factors in stereotype formation." \emph{Stereotypes as explanations: The formation of meaningful beliefs about social groups} Eds. C. McGarty, V. Y. Yzerbyt, and R. Spears. Cambridge: Cambridge University Press, 2002. 1-15. Print.
\paragraph{}
Merali, Zeeya. \emph{Exploding the myth of cultural stereotypes}. 6 Oct. 2005. Web. 2 Jul. 2012. \url{<http://www.newscientist.com/article/dn8111-exploding-the-myth-of-cultural-stereotypes.html>}.
\paragraph{}
Osley, J. and Allan Bird. "Beyond Sophisticated Stereotyping: Cultural Sensemaking in Context". \emph{Academy of Management Executive} 14 (2000): 56-79. 
\paragraph{}
Pickering, Michael. \emph{Stereotyping: The Politics of Representation}. Basingstoke: Palgrave, 2001. Print.
\paragraph{}
Schneider, David. \emph{The Psychology of Stereotyping}. New York: Guilford Press, 2005. Print.
\paragraph{}
Terracciano et al. \emph{National Character Does Not Reflect Mean Personality Trait Levels in 49 Cultures}. Science. 7 (2005): 96-100. Print.
\paragraph{}
Merriam-Webster's Online. \emph{Definition: Stereotype}. Webster's Online Dictionary. 2 Jun. 2012. Web. 8 Jul. 2012. \url{<http://www.merriam-webster.com/medical/stereotype>}.
\paragraph{}
Warlop, Luk. \emph{Stereotypes in Ads}. Consumer Science Group Blog. 3 Oct. 2010. Web. 4 Jul. 2012. \url{<http://econshp2.econ.kuleuven.ac.be/consumerscience/Lists/Posts/Post.aspx?ID=72>}
\paragraph{}
Wikipedia contributors. \emph{Stereotype}. Wikipedia, The Free Encyclopedia, 8 Jul. 2012. Web. 11 Jul. 2012.
\paragraph{}
Wikipedia contributors. \emph{Whisky}. Wikipedia, The Free Encyclopedia, 8 Jul. 2012. Web. 11 Jul. 2012.
